---
title: "Reading Data"
author: "Volha Tryputsen"
date: "October 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(httr)
```

## Scraping

### NSDUH Table

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_xml = read_html(url)
```

That's step one!

```{r}
drug_use_xml %>%
  html_nodes(css = "table")
```

Got the table(s) ...

```{r}
table_marj = (drug_use_xml %>% html_nodes(css = "table"))[[1]] %>%
  html_table() %>%
  .[-1,] %>% 
  as_tibble()
```

Now I have exactly the table I want!!

### NYC Cost of living table

I'd like to understand the impact of my life choices by looking at cost of living in NYC compared to the rest of the US. The table below should help!

```{r}
url = "https://www.bestplaces.net/cost_of_living/city/new_york/new_york"

nyc_cost_xml = read_html(url)

nyc_cost_table = (nyc_cost_xml %>% html_nodes(css = "table"))[[2]] %>% 
  html_table(header = TRUE)
```

### HP_SS Cast

I want the names!!

```{r}
url = "http://www.imdb.com/title/tt0241527/"

hpss_xml = read_html(url)

hpss_cast = hpss_xml %>%
  html_nodes(css = ".itemprop .itemprop") %>% 
  html_text()
```

### Toothbrush reviews

Dental [hygiene](https://www.google.com/search?&rls=en&q=hygiene&ie=UTF-8&oe=UTF-8).

```{r}
url = "https://www.amazon.com/Philips-Sonicare-rechargeable-toothbrush-HX6211/product-reviews/B00YAR7ZFM/ref=cm_cr_arp_d_viewopt_srt?ie=UTF8&reviewerType=all_reviews&sortBy=recent&pageNumber=2"

toothbrush_xml = read_html(url)

toothbrush_titles = toothbrush_xml %>%
  html_nodes(css = "#cm_cr-review_list .review-title") %>% 
  html_text()

toothbrush_stars = toothbrush_xml %>%
  html_nodes(css = "#cm_cr-review_list .review-rating") %>% 
  html_text()

toothbrush_df = data_frame(
  title = toothbrush_titles,
  stars = toothbrush_stars
)

```




## APIs

### Water use data

Getting water data via the API. 

```{r}
nyc_water = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.csv") %>%
  content("parsed")
```

Getting the same data using JSON ...

```{r}
nyc_water = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.json") %>% 
  content("text") %>%
  jsonlite::fromJSON() %>%
  as_tibble()
```

### BRFSS

```{r}
brfss = 
  GET("https://chronicdata.cdc.gov/api/views/hn4x-zwk7/rows.csv?accessType=DOWNLOAD") %>% 
  content("parsed")
```


### Catch the pokemon (data)

```{r}
poke = GET("http://pokeapi.co/api/v2/pokemon/1") %>%
  content()

names(poke)
```
