---
title: "Strings and Factors"
author: "Volha Tryputsen"
date: "October 25, 30, 2017"
output: 
  html_document:
    theme: cosmo
    highlight: haddock
    toc: true
    toc_float:
      collapse: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(haven)
library(rvest)

library(stringr)
library(forcats) #convert character variables into factors
```


# example 1 - PULSE 

* **stringr::str_replace()** - replace matched patterns in a string    
* **forcats::fct_relevel()** - convert string to factor   
* **stringr::str_c()** == paste. Joins multiple strings into a single string   

```{r}
pulse_data = 
  read_sas("./data/public_pulse_data.sas7bdat") %>%
  clean_names() %>%
  gather(key = visit, value = bdi, bdiscore_bl:bdiscore_12m) %>%
  mutate(visit = str_replace(string = visit, pattern = "bdiscore_", replacement = ""), # 
         visit = str_replace(string = visit, pattern = "bl", replace = "00m"),
         visit = fct_relevel(visit, str_c(c("00", "01", "06", "12"), "m"))) %>%
  arrange(id, visit)
```

# example 2 - NSDUH 

1. Scrape the data from the web:    
```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_xml = read_html(url)

table_marj = 
  (drug_use_xml %>% html_nodes(css = "table"))[[1]] %>%
  html_table() %>%
  .[-1,] %>%
  as_tibble()
```

2. Tidy data for analysis:  

* **dplyr::contains()** -  
* **tidyr::separate()** -  
* **stringr::str_sub()** - extract and replace substrings from a character vector    

```{r}
data_marj = 
  table_marj %>%
  select(-contains("P Value")) %>% # removes everything that contains "P Value"
  gather(key = key, value = percent, -State) %>% # convert to long format
  separate(key, into = c("age", "year"), sep = "\\(") %>%
  # keep everything till after the 2nd position from the end. Can aslo do end = 9
  mutate(year = str_sub(string = year, start = 1, end = -2), 
         # replace any letter with the empty space
         percent = str_replace(percent, "[a-z]", ""),
         percent = as.numeric(percent)) %>%
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
```

3. Make a plot:  

* **forcats::fct_reorder()** - reorder levels of the factor  

```{r}
data_marj %>%
  filter(age == "12-17") %>% 
  mutate(State = fct_reorder(State, percent)) %>% 
  ggplot(aes(x = State, y = percent, color = year)) + 
    geom_point() + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r, eval = FALSE}
data_marj %>%
  filter(age == "12-17") %>% 
  mutate(State = fct_reorder(State, percent)) %>%
  pull(State) %>% 
  as.numeric()
```


# example 3 - BMI

This example came up in Lecture 8 (on ANOVA) in Biostatistical Methods I. 

```{r}
ins1 = c(1.53, 1.61, 3.75, 2.89, 3.26)
ins2 = c(3.15, 3.96, 3.59, 1.89, 1.45, 1.56)
ins3 = c(3.89, 3.68, 5.70, 5.62, 5.79, 5.33)
ins4 = c(8.18, 5.64, 7.36, 5.33, 8.82, 5.26, 7.10)
ins5 = c(5.86, 5.46, 5.69, 6.49, 7.81, 9.03, 7.49, 8.98)

bmi_data = data_frame(
    insulin = c(ins1, ins2, ins3, ins4, ins5),
    ind = c(rep(1, length(ins1)),
                    rep(2, length(ins2)),
                    rep(3, length(ins3)),
                    rep(4, length(ins4)),
                    rep(5, length(ins5)))
)
```

We'll recode the `ind` variable to have informative names.

* **for_cats::fct_recode()** - change factor levels by hand    

```{r}
bmi_data = 
  bmi_data %>% 
  mutate(ind = factor(ind), 
         ind = fct_recode(ind,
                          "level_1" = "1",
                          "level_2" = "2",
                          "level_3" = "3",
                          "level_4" = "4",
                          "level_5" = "5")
         )
```

Quick plot shows us what we're dealing with. 

```{r}
bmi_data %>% 
  ggplot(aes(x = ind, y = insulin)) + 
  geom_boxplot()
```

We can also fit a model. 

```{r}
bmi_data %>% 
  lm(insulin ~ ind, data = .) %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable(digits = 3)
```

To see the importance of factor levels, we'll take a look at a different recoding. 

```{r}
bmi_data = bmi_data %>% 
  mutate(ind = fct_recode(ind,
                          "very_low"  = "level_1",
                          "low"       = "level_2",
                          "neutral"   = "level_3",
                          "high"      = "level_4",
                          "very_high" = "level_5"),
         ind = fct_relevel(ind, "neutral"))
```

This recoding makes sense for model fitting ...

```{r}
bmi_data %>% 
  lm(insulin ~ ind, data = .) %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable(digits = 3)
```

... but it doesn't make a lot of sense graphically. 

```{r}
bmi_data %>% 
  ggplot(aes(x = ind, y = insulin)) + 
  geom_boxplot()
```




### NYC Inspections


Load data


```{r}
nyc_inspections = read_csv("./data/DOHMH_New_York_City_Restaurant_Inspection_Results.csv.gz",
                           col_types = cols(building = col_character()),
                           na = c("NA", "N/A"))

nyc_inspections %>% 
  group_by(boro, grade) %>% 
  summarize(n = n()) %>% 
  spread(key = grade, value = n)
```


Cleaning up.

```{r}
nyc_inspections =
  nyc_inspections %>%
  filter(grade %in% c("A", "B", "C"), boro != "Missing") %>% 
  mutate(boro = str_to_title(boro))
```

Search for pizza.

```{r}
nyc_inspections %>% 
  filter(str_detect(dba, "Pizza")) %>% 
  group_by(boro, grade) %>% 
  summarize(n = n()) %>% 
  spread(key = grade, value = n)
```

Better search!

```{r}
nyc_inspections %>% 
  filter(str_detect(dba, regex("pizza", ignore_case = TRUE))) %>% 
  group_by(boro, grade) %>% 
  summarize(n = n()) %>% 
  spread(key = grade, value = n)
```

Make a barplot.

```{r}
nyc_inspections %>% 
  filter(str_detect(dba, regex("pizza", ignore_case = TRUE))) %>%
  ggplot(aes(x = boro, fill = grade)) + geom_bar()
```

Reorder the bar plot ...

```{r}
nyc_inspections %>% 
  filter(str_detect(dba, regex("pizza", ignore_case = TRUE))) %>%
  mutate(boro = fct_infreq(boro)) %>% 
  ggplot(aes(x = boro, fill = grade)) + geom_bar()
```

Here's brooklyn.

```{r}
nyc_inspections %>% 
  filter(str_detect(dba, regex("Pizza", ignore_case = FALSE))) %>%
  mutate(boro = fct_infreq(boro),
         boro = fct_recode(boro, "Hipsterville" = "Brooklyn")) %>%
  ggplot(aes(x = boro, fill = grade)) + geom_bar()
```


